Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-07 verifox.tex
minor and comments
fixes

\textbf{Step 5: Mining Scenario/Transaction Pairs Using Symbolic Execution}
Given a co-verification model, $\mathcal{M}_{seq}$, a scenario, 
$\mathcal{S}$, and a property expressed as $\mathit{assert}(c)$ 
(where $c$ is a condition stated in terms of variables in $\mathcal{M}_{seq}$)
as input, \verifox performs path-based exploration of $\mathcal{M}_{seq}$ 
to automatically infer {\em scencario/transaction} pairs and check their validity 
using backend solvers. If the condition $c$ does not hold, 
then $\mathcal{M}_{seq}$ is said to have violated the property. 
\rmcmt{mark algo with FT and HT scenario transaction pair}

@@

Eager infeasibility check restrict the search to explore
only those FW/HW interations which are feasible under a
given scenario.
%Eager infeasibility check may save the engine from exploring multiple paths
%that emerge through branches encountered after the first point of infeasibility.
In our experiments, we find this optimization has a large effect on runtimes.
Though \verifox poses many queries to the SAT solver, each query is relatively simple due to
two reasons: the resultant formula encodes only a single path, 
and exploration along a path only needs to encode and solve for the path segment (along with the existing
constraints) from the last point of query.

>>>>

\textbf{Step 5: Mining Scenario/Transaction Pairs Using Symbolic Execution}
Given a co-verification model, $\mathcal{M}_{seq}$, a scenario, 
$\mathcal{S}$, and a property expressed as $\mathit{assert}(c)$ 
(where $c$ is a condition stated in terms of variables in $\mathcal{M}_{seq}$)
as input, \verifox performs path-based exploration of $\mathcal{M}_{seq}$ 
to automatically infer {\em scencario/transaction} pairs and check their validity 
using backend solvers. If the condition $c$ does not hold, 
then $\mathcal{M}_{seq}$ is said to have violated the property.

@@

Eager infeasibility check restricts the search to explore
only those FW/HW interations which are feasible under a
given scenario.
%Eager infeasibility check may save the engine from exploring multiple paths
%that emerge through branches encountered after the first point of infeasibility.
In our experiments, we find this optimization has a large effect on runtimes.
Though \verifox poses many queries to the SAT solver, each query is relatively simple due to
two reasons: the resultant formula encodes only a single path, 
and exploration along a path only needs to encode and solve for the path segment (along with the existing
constraints) from the last point of query.
